\hl{On the use of Generative adversarial neural networks for computing photonic crystal fiber optical properties}

### 2020-04-04 docs/paper/paper.tex
WGAN writing is finished

In this section details of the proposed method is discussed. At the start, a GAN is trained to generate additional data by using training samples. These generated samples are filtered to ensure they fall within the applicable range. Original training samples and remaining samples are joined to train a fully-connected feed-forward multi layer perceptron neural network. This architecture is illustrated in Figure \ref{fig:overall}. The details of the proposed ANN architecture and the GAN is discussed in the following subsections.

@@

Generative adversarial networks are introduced in \cite{goodfellow2014generative}. We have employed GAN to augment the number of samples that are used in training. A GAN is composed of two neural networks: estimator and discriminator. The aim of the generator is to transform fully randomized data into data that follows the distribution of the original dataset. Discriminator assesses the performance of the generator and provides feedback for training. Instead of directly training generator, it is trained through this feedback. This paradigm avoids over-fitting the data in the generator side.

It is possible to use different metrics for training in GAN [references here], for this project we have selected WGAN Wasserstein distance metric. This variant has been proposed by Arjovsky et al in \cite{arjovsky2017wasserstein}. In this system, discriminator is named as critic and it measures the distance between the generated data and the real data. The parameters to these networks are given in Table \ref{tbl:gandetails}. The reason behind choosing WGAN over other methods is to be able to determine a stopping criteria. In a regular GAN system, training is stopped when the generated data is deemed viable by an observer. Since GAN is often used in generation of image, video or audio, using a human in the loop is effective. However, in our problem, it is not viable for a human to judge the generated data. Automating this procedure to remove the human in-the-loop can lead to over or under-fitting, which in turn degrades the performance. WGAN uses an adaptive stopping criteria that does not have the issue mentioned above.

Previous works \cite{ravuri2019seeing, shmelkov2018good}, demonstrated that it is possible for random data augmentation to weaken the performance of the model. Hence, it is important to sample the generated data in way to prevent performance degradation \cite{bhattarai2019sampling}. In this method, we use a simple condition to discard the values that fall out of the desired range for both the independent variables ($n_{analyte}, \lambda, \Lambda, d1, d2, d3$), and the confinement loss.

@@

Throughout this paper we will use yet the improved WGAN, the WGAN with Gradient penalty \cite{gulrajani2017improved}. The improved WGAN converges in a stable manner with least efforts made to tune the hyper- parameters of both networks constituting the GAN, which can be very daunting.

In this work, both the Critic and the generator are fully connected feed forward MLP models. Tables(2, 3) summarize the details of both networks. The input vector to the Critic network consists of the six parameters discussed earlier for the ANN model, in addition to the corresponding confinement loss value, giving a total of seven inputs. The generator is supplied with random noise vector having a dimension of $7$, and outputs a vector that resembles that of the input to the Critic.

\begin{figure}
	\centering
	\includegraphics[trim= 0 0 0 0, clip, width=0.9\textwidth]{GAN.png}
	\caption{}
\end{figure}

\begin{table}
	\centering
	\begin{tabular}{l|l|l}
		\textbf{Parameter} & \textbf{Generator} & \textbf{Critic} \\\hline
		Hidden layers & 5 & 5 \\
		Neurons & $ batchsize~2^{2} $ & $batchsize~2^{layers}$ \\
		Activation & ReLU & Leaky ReLU \\
		Optimizer & Adam [ref] & Adam [ref] \\
		Normalization & - & Batch \cite{ioffe2015batch} \\
	\end{tabular}
	\caption{Details of WGAN model}
	\label{tbl:gandetails}
\end{table}

>>>>

In this section details of the proposed method is discussed. Training of the system contains two phases: a GAN phase and regression training phase. At the start of the training, a GAN is trained to generate additional data by using training samples. These generated samples are filtered to ensure they fall within the applicable range. Original training samples and remaining samples are joined to train a fully-connected feed-forward multi layer perceptron neural network. At the end of the training, the ANN that is trained for the regression task will be used to decide the output of a particular input parameters. This architecture is illustrated in Figure \ref{fig:overall}. The details of the proposed ANN architecture and the GAN is discussed in the following subsections.

@@

Generative adversarial networks are introduced in \cite{goodfellow2014generative}. We have employed GAN to augment the number of samples that are used in training. A GAN is composed of two neural networks: generator and discriminator. The aim of the generator is to transform fully randomized data into data that follows the distribution of the original dataset. Discriminator assesses the performance of the generator and provides feedback for training. Instead of directly training generator, it is trained through this feedback. This paradigm avoids over-fitting the data in the generator side.

It is possible to use different metrics for training in GAN [references here], for this project we have selected WGAN Wasserstein distance metric. This variant has been proposed by Arjovsky et al in \cite{arjovsky2017wasserstein}. In this system, discriminator is named as critic and it measures the distance between the generated data and the real data. The reason behind choosing WGAN over other methods is to be able to determine a stopping criteria. In a regular GAN system, training is stopped when the generated data is deemed viable by an observer. Since GAN is often used in generation of image, video or audio, using a human in the loop is effective. However, in our problem, it is not viable for a human to judge the generated data. Automating this procedure to remove the human in-the-loop can lead to over or under-fitting, which in turn degrades the performance. WGAN uses an adaptive stopping criteria that does not have the issue mentioned above. Additionally, we have selected to incorporate Gradient penalty to improve WGAN proposed in \cite{gulrajani2017improved}. This improved WGAN system converges in a stable manner without having to fine tune hyper-parameters of the system. The flowchart of this system is given in Figure \ref{fig:gan}.

In this work, both the Critic and the generator are fully connected feed forward MLP models. The details of the networks are given in Table \ref{tbl:gandetails}. The output from this system should be input and output pairs that will be used to train ANN part of the system. In our PCF system we have 6 input parameters and a single output parameter making a total of 7 parameters that will be used in the GAN phase. In Section \ref{sec:exp}, we have experimented using a different PCF system with different inputs, resulting a different number of parameters for the system. The generator is supplied with the same number of parameters as its expected output, that is 7 for our PCF system. These parameters are generated using Gaussian noise and is called latent variable. Once the training phase is complete, the generator and the filter is used to augment the number of training samples that are available for ANN.

Previous works \cite{ravuri2019seeing, shmelkov2018good}, demonstrated that it is possible for random data augmentation to weaken the performance of the model. Hence, it is important to sample the generated data in way to prevent performance degradation \cite{bhattarai2019sampling}. In the proposed system, we have included a filtering step for the generated data. This step uses a simple condition to discard the values that fall out of the desired range, for both the independent variables ($n_{analyte}, \lambda, \Lambda, d1, d2, d3$), and the confinement loss.

\begin{figure}
	\centering
	\begin{tikzpicture}

	\end{tikzpicture}
	\caption{WGAN architecture}
	\label{fig:gan}
\end{figure}

\begin{table}
	\centering
	\begin{tabular}{l|l|l}
		\textbf{Parameter} & \textbf{Generator} & \textbf{Critic} \\\hline
		Hidden layers & 5 & 5 \\
		Neurons & $ 2^{2}~batchsize $ & $2^{layers}~batchsize$ \\
		Activation & ReLU & Leaky ReLU \\
		Optimizer & Adam [ref] & Adam [ref] \\
		Normalization & - & Batch \cite{ioffe2015batch} \\
	\end{tabular}
	\caption{Details of WGAN model}
	\label{tbl:gandetails}
\end{table}

@@
